manual-geostat-TMB

### 2019-01-22 manual-geostat-TMB.Rmd
annotate manual test

@@

```{r}
survey <- "SYN QCS"

@@

@@

```{r}
#  if (grepl("SYN", survey)) {
    grid_locs <- gfplot:::make_prediction_grid(
      dplyr::filter(dat, year == max(dat$year)), survey = survey,
      cell_width = 2)$grid # cell width of 2 km
    grid_locs <- dplyr::rename(grid_locs, depth = akima_depth)
#  } else {
#    grid_locs <- if (surv == "HBLL OUT N") gfplot::hbll_n_grid$grid else gfplot::hbll_s_grid$grid
 # }
  grid_locs$year <- NULL

@@

```{r}
  spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 100)

@@

```{r}
  predictions <- stats::predict(m, newdata = grid_locs)$data
# predictions$resids <- residuals(m) # randomized quantile residuals but not working
  glimpse(predictions) # est = predicted values

@@

```{r}
#ggplot(predictions, aes(X, Y, col = resids)) + scale_colour_gradient2() +
#  geom_point() + facet_wrap(~year)

@@

```{r}
plot_map(predictions, "exp(est)") +
  scale_fill_viridis_c(trans = "sqrt") +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}

@@

```{r}
plot_map(predictions, "est_re_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2()
```

```{r}
plot_map(predictions, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()

@@

index-standardization

>>>>

#### Load packages

@@

#### Retrieve data
```{r}
survey <- "SYN QCS"

@@

#### Tidy data and fill in missing depth values
```{r}

@@

#### Make prediction grid for plotting
```{r}
#  if (grepl("SYN", survey)) {
    grid_locs <- gfplot:::make_prediction_grid(
      dplyr::filter(dat, year == max(dat$year)), survey = survey,
      cell_width = 2)$grid # cell width of 2 km
    grid_locs <- dplyr::rename(grid_locs, depth = akima_depth)
#  } else {
#    grid_locs <- if (surv == "HBLL OUT N") gfplot::hbll_n_grid$grid else gfplot::hbll_s_grid$grid
 # }
  grid_locs$year <- NULL

@@

#### Spatial model
```{r}
  spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 100)

@@

#### Save preditions from model
```{r}
  predictions <- stats::predict(m, newdata = grid_locs)$data
# predictions$resids <- residuals(m) # randomized quantile residuals but not working
  glimpse(predictions) # est = predicted values

@@

#### Check residuals
```{r}
#ggplot(predictions, aes(X, Y, col = resids)) + scale_colour_gradient2() +
#  geom_point() + facet_wrap(~year)

@@

#### Plot overall model
```{r}
plot_map(predictions, "exp(est)") +
  scale_fill_viridis_c(trans = "sqrt") +
  ggtitle("Prediction (fixed effects + all random effects)")
```

#### Plot fixed effects
```{r}

@@

#### Plot spatial random effects
```{r}
plot_map(predictions, "est_re_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2()
```

#### Plot spatiotemporal random effects
```{r}
plot_map(predictions, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()

@@
